\vskip-0.6in \Large Political Uncertainty

### 2015-12-11 GS-extension.tex
add intuition for pos/neg alpha

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\ga}{\gamma}

@@

@@

\section{Notes from March}
\newpage
Notes from 3/16 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
\end{itemize}

>>>>

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\ga}{\gamma}
\newcommand{\al}{\alpha}

@@

\newpage
\subsection{Intuition}
\begin{itemize}
	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
		\[
		  v(z) = \al - \beta z + a(z) - b(z) > 0
		\]
	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
		\[
		  \al - \beta z - b(z) < 0
		\]

		\begin{center}
		or 
		\end{center}
		\[
		  \beta z - \al + b(z) > 0
		\]
		\item If $\al > 0$, legislators on average are biased against B.
			\begin{itemize}
				\item If $\al < 0$, legislators on average are biased in favor of B.
				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
			\end{itemize}
\end{itemize}

@@

\newpage		
\section{Notes from March}
Notes from 3/16 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
\end{itemize}
